---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nlist

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.com/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/poissonconsulting/nlist.svg?branch=master)](https://travis-ci.com/poissonconsulting/nlist)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/nlist?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/nlist)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/nlist/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/nlist?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

nlist is an R package to create and manipulate numeric list (nlist) objects.
An nlist is an S3 class list of uniquely named numeric atomic (natomic) objects.
An natomic object is an integer or double vector, matrix or array.

Numeric list objects are of interest because they are the raw data inputs for analytic engines such as JAGS, STAN and TMB.

## Demonstration

### `natomic`

An natomic object is an integer or double vector, matrix or array.

```{r}
library(nlist)
is.natomic(TRUE)
is.natomic(1L)
is.natomic(matrix(1:3))
```

### `nlist`

It is straightforward to create an new nlist object.
```{r}
library(nlist)

nlist(x = 1, y = matrix(1:9, 3))
```
Or to coerce an existing object to an nlist.
```{r}
as.nlist(data.frame(lgl = c(TRUE, NA),
                    dte = as.Date(c("2001-01-02", "2001-01-01")),
                    fac = factor(c("b", "a"))))
```

### `nlists`

An nlists object is a S3 class list of nlist objects with the same names, dimensionalities and typeofs.
nlists objects are useful for storing individual realizations of a simulated data set.

```{r}
nlists <- nlists(nlist(x = 1, y = matrix(1:9, 3)), 
                 nlist(x = -2, y = matrix(2:10, 3)))

print(nlists)
```

Aggregating an nlists object gives an nlist object.
```{r}
aggregate(nlists)
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/nlist)
```
remotes::install_github("poissonconsulting/nlist")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)

```
drat::addRepo("poissonconsulting")
install.packages("nlist")
```

## Contribution

Please note that the 'nlist' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
Please note that this project is released with a [Contributor Code of Conduct](https://poissonconsulting.github.io/mcmcr/CONDUCT.html).
By participating in this project you agree to abide by its terms.
