---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nlist

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/nlist)](https://cran.r-project.org/package=nlist)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/nlist)
<!-- badges: end -->

nlist is an R package to create and manipulate numeric list (nlist) objects.

An nlist is an S3 class list of uniquely named numeric atomic (natomic) objects.
An natomic object is an integer or double vector, matrix or array.
nlist objects are the raw data inputs for analytic engines such as JAGS, STAN and TMB.

An nlists object is a S3 class list of nlist objects with the same names, dimensionalities and typeofs.
nlists objects are useful for storing multiple realizations of simulated data sets.
They can be converted to `coda::mcmc` and  `coda::mcmc.list` objects.

## Installation

To install the latest release from [CRAN](https://cran.r-project.org)
```{r, eval=FALSE}
install.packages("nlist")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/nlist)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/nlist")
```

## Demonstration

### `natomic`

An natomic object is an integer or double vector, matrix or array.

```{r}
library(nlist)
is.natomic(TRUE)
is.natomic(1L)
is.natomic(matrix(1:3))
```

### `nlist`

An nlist is an S3 class list of uniquely named numeric atomic (natomic) objects.

It is straightforward to create an new nlist object.
```{r}
library(nlist)

nlist <- nlist(x = 1, y = matrix(1:9, 3))
nlist
```
Or to coerce from a data frame.
```{r}
data <- data.frame(
  lgl = c(TRUE, NA),
  dte = as.Date(c("2001-01-02", "2001-01-01")),
  fac = factor(c("b", "a"))
)

data
as.nlist(data)
```

### `nlists`

An nlists object is a S3 class list of nlist objects with the same names, dimensionalities and typeofs. 
The nchains attribute is used to keep track of the number of chains.

```{r}
nlists <- nlists(
  nlist(x = 1, y = matrix(1:9, 3)),
  nlist(x = -2, y = matrix(2:10, 3)),
  nlist(x = 10, y = matrix(22:30, 3)),
  nlist(x = -100, y = matrix(-2:-10, 3))
)

print(nlists)
```

Aggregating an nlists object gives an nlist object.
```{r}
aggregate(nlists, fun = median)
```

An nlists object can have its chains split or collapsed.
```{r}
nlists <- split_chains(nlists)
```

And can be converted to an mcmc.list object
```{r}
coda::as.mcmc.list(nlists)
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/nlist/issues).

[Pull requests](https://github.com/poissonconsulting/nlist/pulls) are always welcome.

## Code of Conduct

Please note that the nlist project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

