---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nlist

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.com/poissonconsulting/nlist.svg?branch=master)](https://travis-ci.com/poissonconsulting/nlist)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/nlist?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/nlist)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/nlist/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/nlist?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![Tinyverse status](https://tinyverse.netlify.com/badge/nlist)](https://CRAN.R-project.org/package=nlist)
[![CRAN status](https://www.r-pkg.org/badges/version/nlist)](https://cran.r-project.org/package=nlist)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/nlist)
<!-- badges: end -->

nlist is an R package to create and manipulate numeric list (nlist) objects.

An nlist is an S3 class list of uniquely named numeric atomic (natomic) objects.
An natomic object is an integer or double vector, matrix or array.
nlist objects are the raw data inputs for analytic engines such as JAGS, STAN and TMB.

An nlists object is a S3 class list of nlist objects with the same names, dimensionalities and typeofs.
nlists objects are useful for storing multiple realizations of simulated datas sets.
They can be converted to and from `coda::mcmc` objects.

## Installation

To install the latest release version from [CRAN](https://cran.r-project.org)
```r
install.packages("nlist")
```

To install the latest development version from [GitHub](https://github.com/poissonconsulting/hmstimer)
```r
# install.packages("remotes")
remotes::install_github("poissonconsulting/nlist")
```

## Demonstration

### `natomic`

An natomic object is an integer or double vector, matrix or array.

```{r}
library(nlist)
is.natomic(TRUE)
is.natomic(1L)
is.natomic(matrix(1:3))
```

### `nlist`

An nlist is an S3 class list of uniquely named numeric atomic (natomic) objects.

It is straightforward to create an new nlist object.
```{r}
library(nlist)

nlist <- nlist(x = 1, y = matrix(1:9, 3))
nlist
```
Or to coerce from a data frame.
```{r}
data <- data.frame(lgl = c(TRUE, NA),
                    dte = as.Date(c("2001-01-02", "2001-01-01")),
                    fac = factor(c("b", "a")))

data
as.nlist(data)
```

### `nlists`

An nlists object is a S3 class list of nlist objects with the same names, dimensionalities and typeofs.

```{r}
nlists <- nlists(nlist(x = 1, y = matrix(1:9, 3)), 
                 nlist(x = -2, y = matrix(2:10, 3)),
                 nlist(x = -2, y = matrix(2:10, 3)))

print(nlists)
```

Aggregating an nlists object gives an nlist object.
```{r}
aggregate(nlists, FUN = median)
```

An nlists object can be coerced to an coda::mcmc object.
```{r}
coda::as.mcmc(nlists)
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/nlist/issues).

[Pull requests](https://github.com/poissonconsulting/nlist/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/nlist/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms
