---
title: "nlist Objects and Coercions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nlist Objects and Coercions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nlist)
```


## nlist

The central object is the `nlist` object which is an S3 class list of uniquely named numeric objects (which can be integer or double vectors, matrices or arrays).

```{r}
nlist <- nlist(x = 1:2,
               y = c(3L, 4L),
               z = 5.1)
print(nlist)
```

## nlists

`nlist` objects with the same names, dimensionalities and typeofs can be combined to create an `nlists` object.

```{r}
nlists <- nlists(
  nlist,
  nlist,
  nlist(x = 2:3,
        y = c(5L,6L),
        z = 8)
)
print(nlists)
```

## mcmc 

`mcmc` objects which resemble time series (ts) objects are defined by the `coda` package for storing MCMC values.

```{r}
as_mcmc(nlist)
as_mcmc(nlists)
```

`mcmc` objects can be coerced back to `nlist` and `nlists` objects.

```{r}
as_nlist(as_mcmc(nlist))
as_nlists(as_mcmc(nlists))
```
