---
title: "nlist Objects and Coercions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nlist Objects and Coercions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nlist)
```


## nlist

The central object is the `nlist` object which is a list of uniquely named numeric objects (which can be integer or double vectors, matrices or arrays) of class nlist.
`nlist` objects are the raw data inputs for analytic engines such as JAGS, STAN and TMB.

```{r}
nlist <- nlist(
  x = 1:2,
  y = matrix(c(4:1), nrow = 2),
  z = 5.1
)
print(nlist)
str(nlist)
```

## nlists

`nlist` objects with the same names, dimensionalities and typeofs can be combined to create an `nlists` object.
An `nlists` object is a list of `nlist` objects of S3 class `nlists`.
`nlists` objects are useful for storing multiple realizations of simulated data sets (as in the `sims` package) or iterations of MCMC samples of parameter terms output by Bayesian analytic engines such as JAGS and STAN>

```{r}
nlists <- nlists(
  nlist,
  nlist,
  nlist(
    x = 2:3,
    y = matrix(c(5:8), nrow = 2),
    z = 8
  )
)
print(nlists)
str(nlists)
```

## mcmc 

`nlists` (and `nlist`) objects can be converted to `mcmc` objects which are matrices with the parameter terms as the columns and the iterations are the rows.
`mcmc` objects are defined by the `coda` package.

```{r}
as_mcmc(nlist)
as_mcmc(nlists)
str(as_mcmc(nlists))
```

`mcmc` objects can be coerced back to `nlist` and `nlists` objects.

```{r}
as_nlist(as_mcmc(nlist))
as_nlists(as_mcmc(nlists))
```

## list

Unlisting an `nlist` object produces a named vector with the parameter terms as names.

```{r}
unlist(nlist)
```

A vector can be coerced back to an nlist object if an nlist object is available to act as a skeleton.

```{r}
list <- unlist(nlist)
list[1] <- 100
list["z"] <- -999
relist_nlist(list, nlist)
```

## data frame

A `data.frame` of numeric vectors can be coerced to an `nlist` object.

```{r}
as_nlist(data.frame(x = 1:2, y = c(3, 5)))
```

## term frame

And `nlist` and `nlists` object can be converted to a `term_frame`.
A `term_frame` is a data.frame with the parameter terms as one column and the values as another.
In the case of an `nlists` object a sample column is also created specifies the iteration number.

```{r}
as_term_frame(nlist)
as_term_frame(nlists)
```

A `term_frame` object is data.frame.

```{r}
str(as_term_frame(nlists))
```

